---
title: 'DS710 - Assignment #11'
author: "Martin Zanin"
date: "4/8/2018"
output: pdf_document
---
1. In this problem, you will use R to do further analysis on the Amazon reviews data.

a.	In the Python assignment for homework 11, you created a .csv file with information about Amazon reviews.  Use scan() to read this data set into R.

```{r}
AZRev <- scan("AmazonReviews.csv", 
              what = list(NumHelpfulVotes = numeric(),
                          NumVotes = numeric(),
                          Product_ID = character(),
                          Rating = numeric(),
                          ReviewLength = numeric(),
                          NumExclamations = numeric(),
                          HelpfulFraction = numeric()),
                          skip = 1, 
                          nlines = 568454, 
                          sep = ",")

```

b.	Convert the data into a matrix or data frame in which each row represents one review.  Read the header row into R and use it to create column names for the matrix or data frame.
```{r}
AZRevDf <- as.data.frame(AZRev)
AZheader <- scan("AmazonReviews.csv",
                 what = list(NumHelpfulVotes = character(),
                          NumVotes = character(),
                          Product_ID = character(),
                          Rating = character(),
                          ReviewLength = character(),
                          NumExclamations = character(),
                          HelpfulFraction = character()),
                          nlines = 1, 
                          sep = ",")
```

```{r}


```

